---
title: "GymTrainingPredict.rmd"
output: html_document
date: 18 Feb 2017
author: Richie Liew
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background 
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: <http://groupware.les.inf.puc-rio.br/har> (see the section on the Weight Lifting Exercise Dataset).

## Data
The training data for this project are available here:
<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv>

The test data are available here:
<https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv>


## Understanding and Studying the Data
Set working directory
```{r}
setwd("C:/Users/LIEWR/Desktop/rproject/08_Practical_Machine_Learning")
```

# Read in training data set
Read in both training and testing data sets from given sites
```{r}
GymTrainData <- read.csv("./data/pml-training.csv")
GymTestData <- read.csv("./data/pml-testing.csv")
```

# Reduce the length of the variable names associated
This is very important for fast and acurate results
```{r}
attach(GymTrainData)
```

# View a summary of the Classe field data
Take a look at the summary of the dataset
```{r}
table(GymTrainData$classe)
```

# List 33 headings of the data set
Get a rough view of the columns headers
```{r}
head(names(GymTrainData),33)
```

# View some data in Historgram
View a few groupings to get a little understanding of the data
```{r}
par(mfrow=c(2,2))
hist(roll_belt, main = "roll_belt")
hist(roll_forearm, main = "roll_forearm")
hist(roll_arm, main = "roll_arm")
```

## Cleaning and manipulating the Data
### Find out which columns are in Factors

```{r}
ColumnNames <- c()
nCounts = ncol(GymTrainData) - 1
for(i in 1:nCounts) 
{
  if(is.factor(GymTrainData[,i]))
  {
    ColumnNames <- c(ColumnNames, i)
  }
}
```

### Removed all Factor Columns
This will removed factors columns
```{r}
GymTrainData <- GymTrainData[,-ColumnNames]
```

### Removing 1-7 Associations fields which is not needed
The first 7 attibutes will be removed as it is not needed
```{r}
GymTrainData <- GymTrainData[,-c(1,2,3,4,5,6,7)]
```

### Removed all 'NA'
Remove all 'NA' as this does not work in Random Forest algorithm
```{r}
GymTrainData <- GymTrainData[, colSums(is.na(GymTrainData)) == 0]
```

# Using Random Forest to Classify
# Load Random Forest Library
Loading Random Forest Library and Caret Library
```{r}
library(randomForest)
library(caret)
```

# Cross Validation
Cross validation with random sampling and random Forest Algorithm.
```{r}
SeedNum <- 12333
acc2 <- c()
for(i in 1:5)
{
  set.seed(SeedNum)
  SeedNum <- SeedNum+1
  TrainIndex <- createDataPartition(y=GymTrainData$classe, p=0.75, list=FALSE)
  GymTrainSet <- GymTrainData[TrainIndex,]
  GymTestSet <- GymTrainData[-TrainIndex,]
  # Fit in Random Forest Model
  fit <- randomForest(classe ~., data = GymTrainSet, importance = T)
  # Prediction
  prediction <- predict(fit, GymTestSet)
  GymTestSet$rightPred <- prediction == GymTestSet$classe
  t <- table(prediction, GymTestSet$classe)
  print(t)
  # Accuracies
  acc1 <- sum(GymTestSet$rightPred)/nrow(GymTestSet)
  acc2 <- c(acc2, acc1)
  print(acc1)
}
```

Mean accuracy is 0.9910685.
```{r}
mean(acc2)
```

### Classification table
View the classification table
```{r}
table(prediction, GymTestSet$classe)
```

### The Mean Square Error of the random Forest
Plot the mean square error of the forest object
```{r}
plot(fit)
```

### Examine the importance of each attribute within the fitted classifier
```{r}
importance(fit)
```

## Obtain the plot of variable importance
```{r}
varImpPlot(fit)
```

## Applying the Random Forest into 20 Test Cases
```{r}
fit <- randomForest(classe ~., data = GymTrainData)
nrow(GymTestData)
prediction <- predict(fit, GymTestData)
prediction
```