---
title: "Weight Lifting Prediction"
author: "Richie Liew"
date: "November 20, 2016"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

#### The Data

The training data for this project are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

*The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.*
Read more: http://groupware.les.inf.puc-rio.br/har#ixzz4RHrDSCwj

#### How Data Was Gathered

Six young health participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions: exactly according to the specification:

Class | Exercise
--- | ---
Class A | Exactly according to the specification
Class B | Throwing the elbows to the front 
Class C | Lifting the dumbbell only halfway 
Class D | Lowering the dumbbell only halfway 
Class E | Throwing the hips to the front 

Class A corresponds to the specified execution of the exercise, while the other 4 classes correspond to common mistakes. Participants were supervised by an experienced weight lifter to make sure the execution complied to the manner they were supposed to simulate. The exercises were performed by six male participants aged between 20-28 years, with little weight lifting experience. We made sure that all participants could easily simulate the mistakes in a safe and controlled manner by using a relatively light dumbbell (1.25kg).

```{r}


```

###### Assign URL for both dataset.

```{r}
traindata_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testdata_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
```

###### Downloading Training & Test Dataset
```{r}
download.file(traindata_url, "./DATA/traindata.csv")
download.file(testdata_url, "./DATA/testdata.csv")
```

```{r}
# Reading the dataset
train <- read.csv("./DATA/traindata.csv", na.strings = c("", "NA", "#DIV/0!"))
test <- read.csv("./DATA/testdata.csv", na.strings = c("", "NA", "#DIV/0!"))  
```

```{r, results"hide"}
#head(train)
#tail(train)
```













































































































